The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-04-10 paper.tex
submission version

% Abstract of the paper
\begin{abstract}
We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
Only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
galaxies:kinematics and dynamics -- galaxies:evolution -- galaxies:integral field spectroscopy
\end{keywords}

@@

The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie on the red sequence, characterised by red optical colours, low star-formation rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star-formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main-sequence', underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep[e.g.][]{Madau_2014,Khostovan2015}.
At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high redshift, main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.

@@

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between their dark matter halos and baryons, and the subsequent dissipation of this angular momentum (through gravitational collapse, mergers and outflows e.g. \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2017,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotation velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

@@

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `field' environment in which the density of galaxies is typical for this redshift and a `cluster' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal-to-noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal-to-noise across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

@@

%In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
%In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
\noindent
\cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high redshift galaxies (see Appendix \ref{app:kin_error_estimates}).

@@

%\begin{figure*}
%    \centering \hspace{-2.0cm}
%    \begin{subfigure}[h!]{0.50\textwidth}
%        \centering
%        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
%        %\caption{axis ratio distributions}
%    \end{subfigure} \hspace{0.4cm}
%    \begin{subfigure}[h!]{0.50\textwidth}
%        \centering
%        \includegraphics[height=3.6in]{size_distributions.png}
%        %\caption{size distributions}
%    \end{subfigure}
%    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
%    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
%    This suggests that we are not biased towards deriving a particular value for the axis ratio.
%    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
%    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
%    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
%    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
%    \label{fig:morpho-distributions}
%\end{figure*}

@@

\noindent
In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identified signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
In 8/9 resolved KDS cluster galaxies we identified multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas, as well as the morphological and dynamical evolution within these galaxies.
The observation of frequent mergers, which cause major kinematic disturbances, is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
As mentioned above, we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the galaxy continuum maps. 
In the kinematic grids throughout \ref{fig:merger_galaxies} (as well as the bottom grid in \ref{fig:main_body_kinematic_grids}) we present the {\em HST} imaging, kinematic maps and one-dimensional kinematic extractions for the KDS merger candidates in both the field and cluster environments.

@@

\noindent
Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
High redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation. \\

@@

In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean ($z\simeq3$) sample, in the $\sigma_{int}$ vs. $M_{\star}$ plane.
This is an interesting relationship to explore as it has been suggested that rotation velocity alone may not be a good tracer of total dynamical mass at high redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
However, the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
All of these processes are also more prevalent at high redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret. \\

\noindent
We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high redshift.
The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0km\,s^{-1}$, $48.0km\,s^{-1}$ and $85.4km\,s^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20km\,s^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
Generally, the dispersion-dominated galaxies have higher $\sigma_{int}$ values in the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, however the rotation-dominated galaxies also span the full distribution width.

@@

\subsection{The origin and impact of increased velocity dispersions at high redshift}\label{discussion_increase_in_sigma}

@@

Previous studies have claimed that the elevated velocity dispersions observed at high redshift are a consequence of both internal and external processes.
\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.

\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of the order of the galactic half-light radius. 
Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotation velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
Following this, $\sigma_{int}$ decreases over time as ordered rotation begins to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
This is in line with the evolution of gas fractions observed at intermediate and high redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.

@@

\noindent
This relation is an expression of the belief that high redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.

>>>>

% Abstract of the paper
\begin{abstract}
We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high-redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} km\,s^{-1}$, revealing that the increasing average $\sigma_{int}$ with increasing redshift, reported for $z\lesssim2$, continues out to $z\simeq3.5$.
Only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
After carefully selecting comparable star-forming samples at multiple epochs, we find that the rotation-dominated fraction evolves with redshift with a $z^{-0.2}$ dependence. 
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high-redshift galaxies by a combination of the increasing gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and which may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
galaxies:high-redshift ---- galaxies:kinematics and dynamics ---- galaxies:evolution
\end{keywords}

@@

The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie on the red sequence, characterised by red optical colours, low star-formation rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star-formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main-sequence', underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep[e.g.][]{Madau_2014,Khostovan2015}.
At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high-redshift, main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.

@@

Recent cosmological volume simulations provide subgrid recipes for the complex interplay of baryonic processes which are at work as galaxies evolve, and can track the development of individual galaxies from early stages, to maturity and through quenching \citep{Dubois2014,Vogelsberger2014b,Schaye2015}.
Observations can aid the predictive power of such simulations by providing constraints on the evolving physical properties of galaxy populations.
The observed dynamical properties of galaxies contain information about the transfer of angular momentum between their dark matter halos and baryons, and the subsequent dissipation of this angular momentum (through gravitational collapse, mergers and outflows e.g. \citealt{Fall1983,Romanowsky2012,Fall2013}), constituting an important set of quantities for simulations to reproduce.
Developments in both Integral-Field Spectroscopy (IFS) instrumentation and data analysis tools over the last decade have led to the observation of two-dimensional velocity and velocity dispersion fields for large samples of galaxies of different morphological types, spanning a wide redshift range \citep[e.g.][]{Sarzi2005,Flores2006,Epinat2008,ForsterSchreiber2009,Cappellari2011,Gnerucci2011,Epinat2012,Croom2012,Swinbank2012,Swinbank2012a,Bundy2015,Wisnioski2015,Stott2016,Harrison2017,Swinbank2017}.
When interpreted in tandem with high-resolution imaging data from the {\it Hubble Space Telescope (HST)}, these data provide information about the range of physical processes which are driving galaxy evolution.
In particular, in recent years the multiplexing capabilities of KMOS \citep{Sharples2013} have allowed for IFS kinematic observations for large galaxy samples to be assembled rapidly \citep{Sobral2013,Wisnioski2015,Stott2016,Mason2017,Harrison2017} providing an order-of-magnitude boost in statistical power over previous high-redshift campaigns.

@@

There is also an increasing body of work measuring the relationship between the observed maximum rotation velocity of a galaxy, a tracer for the total dynamical mass, and its stellar mass, known as the stellar mass Tully-Fisher Relation (smTFR) \citep{Tully1977}, with surveys reporting disparate results for the evolution of this relation with redshift \citep[e.g.][]{Puech2008,Miller2011,Gnerucci2011,Swinbank2012,Simons2016,Tiley2016,Harrison2017,Straatman2017,Ubler2017}.
Systematic differences in measurement and modelling techniques at high-redshift, especially with regards to beam-smearing corrections, combine with our poor understanding of progenitors and descendants to blur the evolutionary picture which these surveys paint.
Additionally, there has been increasing focus in recent years on whether the measured velocity dispersions track random motions which provide partial gravitational support for high-redshift galaxy disks \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
These random motions may become an increasingly significant component of the dynamical mass budget with increasing redshift \citep{Wuyts2016b} and pressure gradients across the disk could result in a decrease in the observed rotation velocities \citep{Burkert2010}. 
Different interpretations of the gaseous velocity dispersions and their role in providing pressure support against gravity also complicate the evolutionary picture. \\

@@

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The key science goals of the KDS are to investigate the resolved kinematic properties of high-redshift galaxies in the peak epoch of galaxy formation (particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `field' environment in which the density of galaxies is typical for this redshift and a `cluster' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal-to-noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal-to-noise across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

@@

%In the right panel of Figure \ref{fig:morpho-distributions} we plot the distribution of the derived $R_{1/2}$ values (for the 28 galaxies with {\em HST} imaging in the refined sample, \cref{subsubsec:kin_sample_summary}) in comparison to the reference samples spanning two redshift ranges.
%In general the KDS galaxies are much more compact than at lower redshift and overlap with the smaller side of the $3 < z < 4$ reference sample, which we attribute to the lack of massive galaxies in the KDS sample (through the mass-size relation \citep[e.g.][]{Trujillo2004}).
\noindent
\cite{Bruce2012} present a detailed error analysis of the morphological parameters of $1 < z < 3$ galaxies in the CANDELS fields (which includes {\em HST} data covering the GOODS-S field which we exploited during this work), reporting that the magnitude of the error on $R_{1/2}$ is typically at the 10$\%$ level.
We adopted a nominal error of 10$\%$ for our recovered $R_{1/2}$ values and note that the errors on $V_{C}$ and $\sigma_{int}$ are dominated by measurement errors and uncertainties connected with assumptions about the inclination angle correction and the velocity dispersion distribution in high-redshift galaxies (see Appendix \ref{app:kin_error_estimates}).

@@

%\begin{figure*}
%    \centering \hspace{-2.0cm}
%    \begin{subfigure}[h!]{0.50\textwidth}
%        \centering
%        \includegraphics[height=3.5in]{axis_ratio_distributions.png}
%        %\caption{axis ratio distributions}
%    \end{subfigure} \hspace{0.4cm}
%    \begin{subfigure}[h!]{0.50\textwidth}
%        \centering
%        \includegraphics[height=3.6in]{size_distributions.png}
%        %\caption{size distributions}
%    \end{subfigure}
%    \caption{{\it Left:} The normalised counts of KDS galaxies in bins of axis ratio is plotted, along with the normalised counts from the morphological catalogue presented in \protect\cite{VanderWel2012} in two redshift ranges.
%    The axis ratio distribution appears to be constant with time as traced by the reference samples, and the KDS values are in good agreement with a relatively uniform distribution spanning $0.3 < b/a < 0.9$.
%    This suggests that we are not biased towards deriving a particular value for the axis ratio.
%    {\it Right:} The normalised counts of KDS galaxies in bins of half-light radius is plotted, along with the half-light radii of the same \protect\cite{VanderWel2012} galaxies as the left panel.
%    We find that the KDS galaxies are much more compact than those at low redshift, as traced by $R_{1/2}$ measure, which could partially be explained by the F160W filter tracing a younger stellar population at $z\simeq3.5$.
%    The distribution of KDS $R_{1/2}$ values is consistent with the smaller part of the distribution in the high-redshift reference sample, which we attribute to the lack of very massive galaxies in the KDS sample.
%    The extracted velocity values are not sensitive to the exact value of the half-light radius, as the intrinsic rotation curves flatten at small radii (see \protect\ref{fig:main_body_kinematic_grids}).}
%    \label{fig:morpho-distributions}
%\end{figure*}

@@

\noindent
In 6/38 of the resolved KDS field galaxies (one count per merger) we clearly identified signs of multiple components or merging in the {\em HST} high-resolution imaging, which translates into a merger rate of 16\%.
In 8/9 resolved KDS cluster galaxies we identified multiple photometric components, translating into a merger rate of 89\%  (see Table \ref{tab:pointings}).
The higher merger rate observed for the cluster galaxies is perhaps unsurprising since they were drawn from a higher density environment, and these interactions will inevitably have major consequences for the consumption and stripping of gas, as well as the morphological and dynamical evolution within these galaxies.
The observation of frequent mergers, which cause major kinematic disturbances, is also in support of the evidence that galaxies living at the peak of the cosmic density field at lower redshift tend to be redder, less active and morphologically early-type, having presumably rapidly exhausted their gas supply throughout these violent interactions at high-redshifts \citep[e.g.][]{Steidel1998,White2007,Kodama2007,Zheng2009}.
As mentioned above, we omit galaxies in the cluster pointing (SSA22-P1) from the results presented in \cref{sec:results} due to the complexity added by galaxy interactions to the interpretation of cluster galaxy velocity fields.
We keep the KDS galaxies without {\em HST} coverage on the basis that we do not identify double components in the galaxy continuum maps. 
In the kinematic grids throughout \ref{fig:merger_galaxies} (as well as the bottom grid in \ref{fig:main_body_kinematic_grids}) we present the {\em HST} imaging, kinematic maps and one-dimensional kinematic extractions for the KDS merger candidates in both the field and cluster environments.

@@

\noindent
Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
High-redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation. \\

@@

In the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift} we plot the isolated field galaxies, split into dispersion and rotation-dominated classes, along with the AMAZE Clean ($z\simeq3$) sample, in the $\sigma_{int}$ vs. $M_{\star}$ plane.
This is an interesting relationship to explore as it has been suggested that rotation velocity alone may not be a good tracer of total dynamical mass at high-redshift and that random motions traced by $\sigma_{int}$ may contribute to supporting some fraction of this total dynamical mass \citep[e.g.][]{Kassin2007,Burkert2010,Kassin2012,Law2012b,Law2012c,Ubler2017,Genzel2017}.
However, the extent to which the gaseous $\sigma_{int}$ values reported here trace stellar mass is unclear, with physical processes such as disk turbulence, gas accretion and subsequent disk instabilities contributing to the magnitude of the velocity dispersion.
All of these processes are also more prevalent at high-redshift \citep{Genzel2006,ForsterSchreiber2009,Law2009,Genzel2011,Wisnioski2015,Wuyts2016b}, leaving $\sigma_{int}$ as a challenging property to interpret. \\

\noindent
We observe no clear correlation between the gaseous velocity dispersion and stellar mass in any of the sub-samples, highlighting the complicated relationship between these quantities at high-redshift.
The beam-smearing corrected $\sigma_{int}$ values, with distribution median, 16th percentile and 84th percentile equal to $71.0km\,s^{-1}$, $48.0km\,s^{-1}$ and $85.4km\,s^{-1}$ respectively, are larger than in the local universe where typically $\sigma_{int} = 10-20km\,s^{-1}$ \citep{Epinat2008a} (see \cref{subsubsec:sigma_evolution} and \cref{sec:discussion} for a discussion).
Generally, the dispersion-dominated galaxies have higher $\sigma_{int}$ values in the left panel of Figure \ref{fig:sigma_and_v_sigma_w_redshift}, however the rotation-dominated galaxies also span the full distribution width.

@@

\subsection{The origin and impact of increased velocity dispersions at high-redshift}\label{discussion_increase_in_sigma}

@@

Previous studies have claimed that the elevated velocity dispersions observed at high-redshift are a consequence of both internal and external processes.
\cite{Law2009} observe galaxies with elevated velocity dispersions at $z\simeq2.2$ (see Figure \ref{fig:sigma_and_v_sigma_w_redshift}) and attribute this to gravitational instabilities following efficient accretion, which can occur when the cold gas becomes dynamically dominant.

\cite{Genzel2011} show that for dispersion-dominated galaxies, the scales susceptible to gravitational collapse are of the order of the galactic half-light radius. 
Systems such as these form highly unstable and roughly spherical stellar distributions with large internal motions at early times, before more gradual accretion from the galactic halo forms an extended, stable, gaseous disk which instigates kinematic order \citep{Law2009,Genzel2011}.
The physical mechanisms responsible for the increase in $\sigma_{int}$ may also result in a reduction in the observed rotation velocities by partially compensating the gravitational force throughout the galactic disk \citep[e.g.][]{Burkert2010,Wuyts2016b,Ubler2017,Genzel2017,Lang2017}.
Following this, $\sigma_{int}$ decreases over time as ordered rotation begins to dominate and pressure support becomes increasingly insignificant \citep[e.g.][]{Burkert2010,Ubler2017,Genzel2017,Lang2017}.
This is in line with the evolution of gas fractions observed at intermediate and high-redshifts \citep[e.g.][]{Saintonge2013,Tacconi2013,Tacconi2017}, with the gas reservoirs of galaxies fed by the accretion of cold gas.

@@

\noindent
This relation is an expression of the belief that high-redshift galaxies experience more intense and efficient gas inflow, with the accumulation of a more massive stellar population providing stability against perturbations.
In this equilibrium model framework \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}, populations of disk galaxies with higher average stellar mass have lower average velocity dispersions due to this stability condition.
